Supermassive black holes and their host spheroids \\ I. Galaxy vivisection

### 2015-10-16 papers/data_paper/datapaper.tex
grampians

\subsubsection{Image masking}
Galactic stars and any other objects different from the target galaxy 
were masked through a two-step procedure.
First, we created an initial mask using the IRAF task 
{\tt objmasks} that identifies objects by threshold sigma detection.
Then, we refined each mask by hand, using the software 
SAOImage DS9\footnote{SAOImage DS9 development has been made possible by funding 
from the Chandra X-ray Science Center (CXC) 
and the High Energy Astrophysics Science Archive Center (HEASARC).} 
in conjunction with the IRAF task 
{\tt mskregions}. %\footnote{{\tt mskregions} is part of the {\tt proto} package.}.
We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
but also objects overlapping with the target galaxy, such as foreground stars, background galaxies, 
globular clusters or red giant stars.

\subsubsection{1D PSF}
A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained 
$(\alpha, \beta) = (2''.38, 4.39)$.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
%\includegraphics[width=1\columnwidth]{images/star1_cut.eps} \\
%\includegraphics[width=1\columnwidth]{images/PRF_IRACch1_129_129_cut.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (bottom panel) 
and of the IRAC instrument Point Response Function (PRF, top panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/n2974_imgmsk.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_unsharp.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_model.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
\caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
unsharp mask (second panel, {\bf on a linear scale}), 
best-fit 2D model (third panel, {\bf on a logarithmic scale}), 
and residual image after the subtraction of the 2D model (bottom panel, {\bf on a linear scale; 
the residual patterns correspond to differences between the data and the model of less than 6\%}).
The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
\label{fig:n29742d}
\end{center}
\end{figure}

\section{Results}
\label{sec:res}
For each galaxy, after we identified its various components and built a model accordingly, 
we simultaneously performed a set of four 1D fits.
All four fits use a Moffat-convolved model.
Two fits use the major-axis surface brightness profile and the remaining two use the equivalent-axis surface brightness profile. 
For each of these pairs, we use a logarithmically sampled surface brightness profile 
and a linearly sampled surface brightness profile. 
Because our fitting routine intentionally does not employ an error weighting scheme on the data points that constitute the surface brightness profile, 
a fit to a logarithmically sampled profile puts more weight on the inner region of the galaxy 
and poorly constrains the outskirts.
On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions, 
but is more susceptible to sky-background subtraction issues. \\ 
We found that the fits are, in general, more sensitive to the choice of the initial parameters 
when using logarithmically sampled profiles than linearly sampled profiles. 
In addition, a visual examination of the residuals revealed that the quality of the fit within one galaxy effective radius 
is superior when tighter constraints are put on the galaxy outskirts.
In other words, the better quality of the residuals led us to prefer the fits that use linearly sampled surface brightness profiles,
although the results were ususally very similar,as might be expected. \\
Among the initial sample of 75 galaxies, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
The first two have been stripped by their massive companions, and thus have uncertain morphology. 
The Circinus Galaxy lies at only 4 degrees from the Galactic Plane, 
therefore its image mosaic is contaminated by a large number of foreground stars.
Of the remaining 72 galaxies, 
we obtained satisfactory 1D decompositions for 66, 
whereas the models of 6 galaxies were judged not reliable and were thus excluded. 
We also performed reliable 2D decompositions for 31 galaxies. \\
A galaxy-by-galaxy comparison between our best-fit models and those from the previous literature 
helped identify the optimal decompositions and past problems. 
We compared our best-fit models with those of \cite{grahamdriver2007}, \cite{sani2011}, \cite{beifiori2012}, 
\cite{vika2012} and \cite{lasker2014data}. 
We also considered the best-fit models of \cite{laurikainen2010} and \cite{rusli2013} because,   
although they did not specifically deal with black hole -- galaxy scaling relations, 
their galaxy samples significantly overlap with ours. \\
%In Section \ref{sec:indgal} we discuss individual cases, explaining the discrepancies between different decompositions. \\
Table \ref{tab:fitres} lists the results from both the 1D and 2D fits.

@@

\subsection{1D versus 2D decompositions}
Here we explore how 1D and 2D decompositions compare with each other. 
Readers not interested in our practical knowledge, 
having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
We summarize our experience in the following points:
\begin{itemize}
\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
Weak bars and some embedded disks can easily be missed. 
Other (inclined) embedded disks can be confused with large-scale disks.
In this regards, the 1D isophotal analysis is extremely helpful. 
Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
about a galaxy's constituents.
\item The ellipticity and position angle of triaxial spheroids can vary with radius.
The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
thus they cannot account for these radial gradients. 
This problem is overcome with 1D decomposition techniques 
{\bf because the ellipticity, and additionally the deviations from elliptical isophotes, 
are efficiently included in the equivalent-axis fit (see the Appendix of \citealt{ciambur2015})}.
\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
\end{itemize}
Although we attempted 2D modeling for the 72 galaxies in our sample, 
more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
This should serve as a tip to users of 2D fitting codes. 
When physically meaningful spheroid parameters are required, 
the output may not be reliable and should be inspected.
For the 31 galaxies that had successful 2D decompositions, 
we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
%The software \textsc{Imfit} returns major-axis measurements of effective radii, 
%which are plotted in Figure \ref{fig:re1d2d} versus the corresponding 1D major-axis measurements.
%2D measurements of S\'ersic indices can be approximated to 1D equivalent-axis measurements, 
%and are therefore compared to them in Figure \ref{fig:n1d2d}.
%Figure \ref{fig:mag1d2d} shows 2D versus 1D measurements of bulge magnitudes. 
The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
No systematic effects are observed in any of these three plots, 
which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
can give consistent results. \\
In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
and given that we obtained more successful 1D decompositions than 2D, 
we will base our analysis on the results from the 1D fits.

@@

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
\caption{Bottom panel: 58 galaxies for which at least one measurement of the spheroid S\'ersic index $n_{\rm sph}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(n_{\rm sph}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
Each data point corresponds to an individual measurement from: 
\citeauthor{grahamdriver2007}~(\citeyear{grahamdriver2007}, red points);  
\citeauthor{laurikainen2010}~(\citeyear{laurikainen2010}, blue points); 
\citeauthor{sani2011}~(\citeyear{sani2011}, green points);  
\citeauthor{vika2012}~(\citeyear{vika2012}, yellow points);
\citeauthor{beifiori2012}~(\citeyear{beifiori2012}, gray points); 
\citeauthor{rusli2013}~(\citeyear{rusli2013}, white points); 
\citeauthor{lasker2014data}~(\citeyear{lasker2014data}, orange points). 
Black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to the measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively, 
corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres} (see Section \ref{sec:err} for details).
We consider these to be absolute upper limits to the uncertainty on our parameters 
given the care we have taken to minimise sources of systematic errors. }
\label{fig:compn}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
\caption{Bottom panel: 52 galaxies for which at least one measurement of the spheroid major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compre}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
\caption{Bottom panel: 51 galaxies for which at least one measurement of the spheroid apparent magnitude $m_{\rm sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
The average value $\langle m_{\rm sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmag}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid effective surface brightness $\mu_{\rm e,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm e,sph} \rangle$ from all fits to a galaxy, 
not to be confused with the mean effective surface brightness within $R_{\rm e,sph}$, is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmue}
\end{center}
\end{figure}

\begin{figure}%[h]
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid central surface brightness $\mu_{\rm 0,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm 0,sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmu0}
\end{center}
\end{figure}

@@

\begin{table*}%[ht] 
\begin{center}  				      
\caption{Summary of previous investigations of black hole mass scaling relations} 
\begin{tabular}{lllllll}
\hline
              & {\bf GD07}  & {\bf S+11}   & {\bf V+12} & {\bf B+12}   & {\bf L+14} & {\bf This work}	      \\ %%[0.5ex] 
\hline
{\bf Galaxies with successful fit} & 27		     & 57	       & 25      & 19          & 35      & 66               \\
{\bf Wavelength}        	   & $R$-band	     & $3.6~\rm \mu m$ & $K$-band& $i$-band    & $K$-band& $3.6~\rm \mu m$  \\
{\bf Decomposition}     	   & 1D 	     & 2D	       & 2D	 & 2D	       & 2D	 & 1D \& 2D	    \\
{\bf Nuclear components}       	   & masked	     & modeled         & modeled & not treated & modeled & modeled/masked   \\
{\bf Partially depleted cores} 	   & masked	     & masked	       & masked  & not treated & masked  & masked	    \\ 
{\bf Bars}	        	   & excluded	     & modeled         & modeled & excluded    & modeled & modeled	    \\ 
{\bf Other components}  	   & no 	     & no 	       & no	 & no	       & yes	 & yes  	    \\ 
{\bf Kinematics}        	   & no 	     & no	       & no	 & no	       & no	 & yes  	    \\ %%[0.5ex] 
\hline 
\end{tabular}
\label{tab:lit} 
\tablecomments{GD07 = \cite{grahamdriver2007}, 
S+11 = \cite{sani2011}, V+12 \cite{vika2012}, B+12 = \cite{beifiori2012}, L+14 = \cite{lasker2014data}.}
\end{center}	
\end{table*}

@@

%{\bf Lasker's conclusions are: bulge+disk decompositions are not enough, we do better by adding bars, spiral arms and stuff (really?? what a surprising conclusion);
%we modelled the envelope of 5 galaxies; we observed central light deficits in 9 ellipticals; total magnitudes are independent from details of modelling (no, really?)
%and bulge magnitudes are 0.36 mag fainter when additional components (other than bulge and disk) are modelled.  }

%\clearpage

\acknowledgments
GS acknowledges the invaluable support received from Alessandro Marconi, Eleonora Sani and Leslie Hunt 
in the early stages of this research.
GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Giuseppe Gavazzi, 
Bililign Dullo, Paolo Bonfini, Elisabete Lima Da Cunha 
and Gonzalo Diaz 
for useful discussion. \\
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
  \caption{IC 1459: 
  An elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
  nuclear dust and indications of a nuclear stellar disk \citep{forbes1994ic1459}.
  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
  This galaxy also has an unresolved partially depleted core \citep{rusli2013}.  % ($R_{\rm break} = 0''.69$, \citealt{rusli2013}).
  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
  After masking the innermost $6''.1$, we fit this galaxy with a S\'ersic profile.  }
  \end{center}
  \end{figure}

>>>>

\subsubsection{Image masking}
Galactic stars and any other objects different from the target galaxy 
were masked through a two-step procedure.
First, we created an initial mask using the IRAF task 
{\tt objmasks} that identifies objects by threshold sigma detection.
Then, we refined each mask by hand, using the software 
SAOImage DS9\footnote{SAOImage DS9 development has been made possible by funding 
from the Chandra X-ray Science Center (CXC) 
and the High Energy Astrophysics Science Archive Center (HEASARC).} 
in conjunction with the IRAF task 
{\tt mskregions}. 
We identified and carefully masked not only contaminating sources located in the field of the image mosaic,
but also objects overlapping with the target galaxy, such as foreground stars, background galaxies, 
globular clusters or red giant stars.

\subsubsection{1D PSF}
A universal\footnote{\bf Across all mosaics, the variation of the Moffat $FWHM$ is $\pm 0''.1$, 
and the variation of the Moffat $\beta$ is $\pm 2.0$.
The use of a universal PSF is justified for the following reasons: 
\emph{i}) the PSF-convolution is more sensitive to the value of the $FWHM$ than $\beta$, 
i.e. having a 50\% variation in $\beta$ is not an issue as long as the variation in $FWHM$ is small;
\emph{ii}) the use of a non-signal-to-noise-weighted fitting scheme minimizes biases from a non-accurate PSF description;
\emph{iii}) not all mosaics have enough stars suitable for the PSF characterization: 
rather than having an individual PSF for each mosaic (which would have been based on only 1-2 stars for some mosaics), 
we preferred the use of a universal PSF.}, 
average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \cite{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained 
$(\alpha, \beta) = (2''.38, 4.39)$.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\columnwidth, trim = 240 40 50 20, clip=True]{images/psf.eps}
\caption{Normalized flux versus radial distance 
from the image centroid of an observed point source (bottom panel) 
and of the IRAC instrument Point Response Function (PRF, top panel). 
The normalized flux is given in arbitrary units, 
and the radial distance is in units of pixel size of the IRAC detector (1 pixel = $1''.22$).
The blue solid line shows our 1D Moffat PSF model,
which has been normalized to intersect the data point with the largest flux. 
The $FWHM$ of the IRAC PRF is clearly smaller than that of a ``real'' star.
The inserts display the images of the observed point source and the IRAC PRF.}
\label{fig:psf}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/n2974_imgmsk.eps}
\includegraphics[width=\columnwidth]{images/n2974_unsharp.eps}
\includegraphics[width=\columnwidth]{images/n2974_model.eps}
\includegraphics[width=\columnwidth]{images/n2974_resid.eps}
\caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
unsharp mask (second panel, {\bf on a linear scale}), 
best-fit 2D model (third panel, {\bf on a logarithmic scale}), 
and residual image after the subtraction of the 2D model (bottom panel, {\bf on a linear scale; 
the residual patterns correspond to differences between the data and the model of less than 6\%}).
The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
\label{fig:n29742d}
\end{center}
\end{figure}

\section{Results}
\label{sec:res}
For each galaxy, after we identified its various components and built a model accordingly, 
we simultaneously performed a set of four 1D fits.
All four fits use a Moffat-convolved model.
Two fits use the major-axis surface brightness profile and the remaining two use the equivalent-axis surface brightness profile. 
For each of these pairs, we use a logarithmically sampled surface brightness profile 
and a linearly sampled surface brightness profile. 
Because our fitting routine intentionally does not employ an error weighting scheme on the data points that constitute the surface brightness profile, 
a fit to a logarithmically sampled profile puts more weight on the inner region of the galaxy 
and poorly constrains the outskirts.
On the other hand, a fit to a linearly sampled surface brightness profile equally treats inner and outer regions, 
but is more susceptible to sky-background subtraction issues. \\ 
We found that the fits are, in general, more sensitive to the choice of the initial parameters 
when using logarithmically sampled profiles than linearly sampled profiles. 
In addition, a visual examination of the residuals revealed that the quality of the fit within one galaxy effective radius 
is superior when tighter constraints are put on the galaxy outskirts.
In other words, the better quality of the residuals led us to prefer the fits that use linearly sampled surface brightness profiles,
although the results were ususally very similar,as might be expected. \\
Among the initial sample of 75 galaxies, we did not attempt to model 3 galaxies: M32, NGC 4486A and the Circinus Galaxy. 
The first two have been stripped by their massive companions, and thus have uncertain morphology. 
The Circinus Galaxy lies at only 4 degrees from the Galactic Plane, 
therefore its image mosaic is contaminated by a large number of foreground stars.
Of the remaining 72 galaxies, 
we obtained satisfactory 1D decompositions for 66, 
whereas the models of 6 galaxies were judged not reliable and were thus excluded. 
We also performed reliable 2D decompositions for 31 galaxies. \\
A galaxy-by-galaxy comparison between our best-fit models and those from the previous literature 
helped identify the optimal decompositions and past problems. 
We compared our best-fit models with those of \cite{grahamdriver2007}, \cite{sani2011}, \cite{beifiori2012}, 
\cite{vika2012} and \cite{lasker2014data}. 
We also considered the best-fit models of \cite{laurikainen2010} and \cite{rusli2013} because,   
although they did not specifically deal with black hole -- galaxy scaling relations, 
their galaxy samples significantly overlap with ours. \\
Table \ref{tab:fitres} lists the results from both the 1D and 2D fits.

@@

\subsection{1D versus 2D decompositions}
Here we explore how 1D and 2D decompositions compare with each other. 
Readers not interested in our practical knowledge, 
having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
We summarize our experience in the following points:
\begin{itemize}
\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
Weak bars and some embedded disks can easily be missed. 
Other (inclined) embedded disks can be confused with large-scale disks.
In this regards, the 1D isophotal analysis is extremely helpful. 
Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
about a galaxy's constituents.
\item The ellipticity and position angle of triaxial spheroids can vary with radius.
The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
thus they cannot account for these radial gradients. 
This problem is overcome with 1D decomposition techniques 
{\bf because the ellipticity, and additionally the deviations from elliptical isophotes, 
are efficiently included in the equivalent-axis fit (see the Appendix of \citealt{ciambur2015})}.
\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
\end{itemize}
Although we attempted 2D modeling for the 72 galaxies in our sample, 
more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
This should serve as a tip to users of 2D fitting codes. 
When physically meaningful spheroid parameters are required, 
the output may not be reliable and should be inspected.
For the 31 galaxies that had successful 2D decompositions, 
we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
No systematic effects are observed in any of these three plots, 
which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
can give consistent results. \\
In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
and given that we obtained more successful 1D decompositions than 2D, 
we will base our analysis on the results from the 1D fits.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_n.eps} 
\caption{Bottom panel: 58 galaxies for which at least one measurement of the spheroid S\'ersic index $n_{\rm sph}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(n_{\rm sph}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
Each data point corresponds to an individual measurement from: 
\citeauthor{grahamdriver2007}~(\citeyear{grahamdriver2007}, red points);  
\citeauthor{laurikainen2010}~(\citeyear{laurikainen2010}, blue points); 
\citeauthor{sani2011}~(\citeyear{sani2011}, green points);  
\citeauthor{vika2012}~(\citeyear{vika2012}, yellow points);
\citeauthor{beifiori2012}~(\citeyear{beifiori2012}, gray points); 
\citeauthor{rusli2013}~(\citeyear{rusli2013}, white points); 
\citeauthor{lasker2014data}~(\citeyear{lasker2014data}, orange points). 
Black points are measurements obtained from the 1D fits presented in this work 
(using linearly sampled surface brightness profiles, along the major-axis).
In the top panel, the white histogram shows the distribution of $\log(n_{\rm sph}) - \langle \log(n_{\rm sph}) \rangle$ 
for all measurements, 
whereas the black histogram refers only to the measurements obtained by us.
The (asymmetric) error bars $\sigma_1$, $\sigma_2$ and $\sigma_3$ enclose 38\%, 78\% and 92\% 
of the black histogram, respectively, 
corresponding to our quality flags 1, 2 and 3 given in Table \ref{tab:fitres} (see Section \ref{sec:err} for details).
We consider these to be absolute upper limits to the uncertainty on our parameters 
given the care we have taken to minimise sources of systematic errors. }
\label{fig:compn}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_r_e.eps} 
\caption{Bottom panel: 52 galaxies for which at least one measurement of the spheroid major-axis effective radius $R_{\rm e}^{\rm maj}$ is available 
from the literature (Table \ref{tab:lit}), in addition to that measured by us.
The average (logarithmic) value $\langle \log(R_{\rm e}^{\rm maj}) \rangle$ is plotted against 
the difference between (the logarithm of) the individual measurements of a galaxy 
and the average (logarithmic) value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compre}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mag_sph.eps} 
\caption{Bottom panel: 51 galaxies for which at least one measurement of the spheroid apparent magnitude $m_{\rm sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $3.6~\rm \mu m$ magnitudes were converted into $K$-band magnitudes (see Section \ref{sec:err} for details).
The average value $\langle m_{\rm sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmag}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_e.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid effective surface brightness $\mu_{\rm e,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm e,sph} \rangle$ from all fits to a galaxy, 
not to be confused with the mean effective surface brightness within $R_{\rm e,sph}$, is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmue}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=1.1\columnwidth]{images/comparison_all_mu_0.eps} 
\caption{Bottom panel: 49 galaxies for which at least one measurement of the spheroid central surface brightness $\mu_{\rm 0,sph}$ 
-- either in the $K$-band or at $3.6~\rm \mu m$ -- is available from the literature (Table \ref{tab:lit}), in addition to that measured by us. 
The $K$-band magnitudes were converted into $3.6~\rm \mu m$ magnitudes (see Section \ref{sec:err} for details).
The average value $\langle \mu_{\rm 0,sph} \rangle$ is plotted against 
the difference between the individual measurements of a galaxy 
and the average value for that same galaxy.
See Figure \ref{fig:compn} for color description and explanation of the top panel.}
\label{fig:compmu0}
\end{center}
\end{figure}

@@

\begin{table*}
\begin{center}  				      
\caption{Summary of previous investigations of black hole mass scaling relations} 
\begin{tabular}{lllllll}
\hline
              & {\bf GD07}  & {\bf S+11}   & {\bf V+12} & {\bf B+12}   & {\bf L+14} & {\bf This work}	      \\ 
\hline
{\bf Galaxies with successful fit} & 27		     & 57	       & 25      & 19          & 35      & 66               \\
{\bf Wavelength}        	   & $R$-band	     & $3.6~\rm \mu m$ & $K$-band& $i$-band    & $K$-band& $3.6~\rm \mu m$  \\
{\bf Decomposition}     	   & 1D 	     & 2D	       & 2D	 & 2D	       & 2D	 & 1D \& 2D	    \\
{\bf Nuclear components}       	   & masked	     & modeled         & modeled & not treated & modeled & modeled/masked   \\
{\bf Partially depleted cores} 	   & masked	     & masked	       & masked  & not treated & masked  & masked	    \\ 
{\bf Bars}	        	   & excluded	     & modeled         & modeled & excluded    & modeled & modeled	    \\ 
{\bf Other components}  	   & no 	     & no 	       & no	 & no	       & yes	 & yes  	    \\ 
{\bf Kinematics}        	   & no 	     & no	       & no	 & no	       & no	 & yes  	    \\  
\hline 
\end{tabular}
\label{tab:lit} 
\tablecomments{GD07 = \cite{grahamdriver2007}, 
S+11 = \cite{sani2011}, V+12 \cite{vika2012}, B+12 = \cite{beifiori2012}, L+14 = \cite{lasker2014data}.}
\end{center}	
\end{table*}

@@

\acknowledgments
GS acknowledges the invaluable support received from Alessandro Marconi, Eleonora Sani and Leslie Hunt 
in the early stages of this research.
GS warmly thanks Chieng Peng, Peter Erwin, Luca Cortese, Giuseppe Gavazzi, 
Bililign Dullo, Paolo Bonfini, Elisabete Lima Da Cunha 
and Gonzalo Diaz 
for useful discussion. 
{\bf We thank the anonymous referee for their thorough review and highly appreciate the comments and suggestions, 
which significantly contributed to improving the quality of the publication. } \\
This research was supported by Australian Research Council funding through grants
DP110103509 and FT110100263.
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} 
on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, 
California Institute of Technology under a contract with NASA.
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/ic1459_1Dfit.eps}
  \caption{IC 1459: 
  An elliptical galaxy with a fast counterrotating stellar component \citep{franxillingworth1988ic1459,cappellari2002ic1459},
  nuclear dust and indications of a nuclear stellar disk \citep{forbes1994ic1459}.
  The kinematically decoupled component cannot be identified as a separate structure in photometric observations.
  This galaxy also has an unresolved partially depleted core \citep{rusli2013}.  
  Our isophotal analysis confirms a simple morphology for IC 1459, with no evident embedded components.
  After masking the innermost $6''.1$, we fit this galaxy with a S\'ersic profile.  }
  \end{center}
  \end{figure}
